Moral Foundations of U.S. Political News Organizations

### 2024-11-30 manuscript_version/revision/revision_letter.Rmd
finalizing the revision letter and manuscript

Thank you very much for taking the time to consider our manuscript for publication at _`r rmarkdown::metadata$journal`_.

@@

The section in the literature review describing the Frimer study has been expanded like shown below.

“Beyond the critiques of the theory itself, many have also provided strong critiques of the measurement using MFD. Conducting two close conceptual replication studies using religious sermons and six extension studies using U.S. Congressional speeches, party platforms, State of the Union addresses, media outlets, and political organization texts, @Frimer2020 found that the liberal-conservative differences found in the original study replicated in only 30% of cases and the effect sizes were over 30 times smaller than reported in @Graham2009. In a meta-analysis, the theorized differences were only found for authority and purity (e.g., conservatives used more authority and purity words). Loyalty was contrary to theoretical predictions (e.g., used more by liberals), and no differences were found for harm and fairness. Additionally, @Frimer2020 tested the theory under the most forgiving conditions using not only the original MFD but also the revised MFD2 as well using log transformed scores as well as raw scores. Even under the best circumstances (log transformed MFD2 scores), only 2 of the foundations showed theorized differences but with very small effects… Like @Frimer2020, we attempt to give the MFD the best chance for success by incorporating a weighting method to address the skewedness and sparsity of the linguistic data.”

@@

Given no page limits for the manuscript, we have opted to include this detail for transparency and openness purposes within the manuscript. Linguistic analysis heavily relies on the pre-processing steps taken on the data, and informing readers on these actions can help contextualize interpretation. We have streamlined in method sections when it was repetitive refering back to previous studies.

@@

We added an example table of the weighting calculation and rephrased this section completely for clarity.

"A complete list of the words for each moral foundation area was created from previous experiments. The total number of times each of those words was used in an article was calculated. This information was merged with the valence values from the @Warriner2013 dataset. A weighted score was calculated by multiplying the frequency of occurrence within a document times the *z*-scored valence values and divided by the word count for that article. The final score was multiplied by 100 to represented a weighted percentage. Finally, the weighted scores were summed within in each article to get a total weighted percentage of the use of moral area specific words by article."

Unfortunately, as with many linguistic analyses that focus on individual words (as with the MFD), context is lost using these approaches.

In response to the question about analytic choices, we have added information about a MTMM study (study 1), as well as the exact same statistics using the mean percentages for comparison (study 2-3). The results remain the same.

>>>>

Thank you very much for taking the time to consider our manuscript for publication at _`r rmarkdown::metadata$journal`_. Because we made a large number of changes to the document as requested, we do not copy all the changes here, but note a few specific areas. We believe the manuscript is much improved and thank the reviewers for their thoughtful commments.

@@

The section in the literature review describing the Frimer study has been expanded to fully describe the study.

@@

We have streamlined in method sections when it was repetitive refering back to previous studies. We did keep places in which analyses were different or otherwise it was necessary for clarity (given the other reviewers comments).

@@

We added an example table of the weighting calculation and rephrased this section completely for clarity. Unfortunately, as with many linguistic analyses that focus on individual words (as with the MFD), context is lost using these approaches.

In response to the question about analytic choices, we have added information about a MTMM study (study 1), as well as the exact same statistics using the mean percentages for comparison (study 2-3). We believe these additions will allow for comparison of different approaches versus the normal approach and the validity evidence for the MFD.
